Report and Figures

### 2016-11-10 figs.Rmd
non-binary loss curves

>>>>

adjust_thresh = 0.01
highlights  <- c('Philadelphia', 'Atlanta', 'Detroit')
curves <- loss_curves %>% 
  mutate(exclude = (nclust != 1) & (cummax(I_XY - lag(I_XY,default = 0)) < adjust_thresh) & (nclust < 10)) %>% 
	filter(!exclude,
	       max(I_XY > 0.0)) %>%
	mutate(nclust = row_number())

  ggsave('figs/loss_curves.pdf', width = 7, height = 4)
  embed_fonts("figs/loss_curves.pdf", outfile="figs/loss_curves.pdf")
